Effect of quality-adjusted production function inputs

### 2015-05-12 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Trying to create formulas in a loop.

<<Time Series Variables>>=
# This block of code sets up the time-series variables 
# to be used for each country.
# Adding this level of abstraction makes it easier 
# for us to change variables later.
# It also makes it easier to see what is going on 
# in each formula throughout the document.
# Use of substitute establishes an R "name"
# that can be a component of a formula.
# Economic output
y_PT <- substitute(iGDP)
y_UK <- substitute(iGDP)
# Portugal undajusted inputs
k_PT_unadj <- substitute(iKstkS.L)
l_PT_unadj <- substitute(iL)
e_PT_unadj <- substitute(iXpMP)
# Portugal quality-adjusted inputs
k_PT_adj <- substitute(iKservS.L)
l_PT_adj <- substitute(ihLest)
e_PT_adj <- substitute(iUMP)
# UK unadjusted inputs
k_UK_unadj <- substitute(iKstkO.WwithRD)
l_UK_unadj <- substitute(iL)
e_UK_unadj <- substitute(iXp)
# UK quality-adjusted inputs
k_UK_adj <- substitute(iKservO.WwithRD)
l_UK_adj <- substitute(ihLest)
e_UK_adj <- substitute(iU)
# Time variables
t_PT <- substitute(iYear)
t_UK <- substitute(iYear)

>>>>

<<Time Series Variables>>=
# This block of code sets up the time-series variables 
# to be used for each country.
# Adding this level of abstraction makes it easier 
# for us to change variables later.
# It also makes it easier to see what is going on 
# in each formula throughout the document.
# Use of substitute establishes an R "name"
# that can be a component of a formula.
# # Economic output
# y_PT <- substitute(iGDP)
# y_UK <- substitute(iGDP)
# # Portugal undajusted inputs
# k_PT_unadj <- substitute(iKstkS.L)
# l_PT_unadj <- substitute(iL)
# e_PT_unadj <- substitute(iXpMP)
# # Portugal quality-adjusted inputs
# k_PT_adj <- substitute(iKservS.L)
# l_PT_adj <- substitute(ihLest)
# e_PT_adj <- substitute(iUMP)
# # UK unadjusted inputs
# k_UK_unadj <- substitute(iKstkO.WwithRD)
# l_UK_unadj <- substitute(iL)
# e_UK_unadj <- substitute(iXp)
# # UK quality-adjusted inputs
# k_UK_adj <- substitute(iKservO.WwithRD)
# l_UK_adj <- substitute(ihLest)
# e_UK_adj <- substitute(iU)
# # Time variables
# t_PT <- substitute(iYear)
# t_UK <- substitute(iYear)

# vars <- list()
# # Economic output
# vars$y.PT <- substitute(iGDP)
# vars$y.UK <- substitute(iGDP)
# # Portugal undajusted inputs
# vars$k.PT.unadj <- substitute(iKstkS.L)
# vars$l.PT.unadj <- substitute(iL)
# vars$e.PT.unadj <- substitute(iXpMP)
# # Portugal quality-adjusted inputs
# vars$k.PT.adj <- substitute(iKservS.L)
# vars$l.PT.adj <- substitute(ihLest)
# vars$e.PT.adj <- substitute(iUMP)
# # UK unadjusted inputs
# vars$k.UK.unadj <- substitute(iKstkO.WwithRD)
# vars$l.UK.unadj <- substitute(iL)
# vars$e.UK.unadj <- substitute(iXp)
# # UK quality-adjusted inputs
# vars$k.UK.adj <- substitute(iKservO.WwithRD)
# vars$l.UK.adj <- substitute(ihLest)
# vars$e.UK.adj <- substitute(iU)
# # Time variables
# vars$t.PT <- substitute(iYear)
# vars$t.UK <- substitute(iYear)

y <- list()
k <- list()
l <- list()
e <- list()
t <- list()
# Economic output
y$PT <- substitute(iGDP)
y$UK <- substitute(iGDP)
# Portugal undajusted inputs
k$PT$unadj <- substitute(iKstkS.L)
l$PT$unadj <- substitute(iL)
e$PT$unadj <- substitute(iXpMP)
# Portugal quality-adjusted inputs
k$PT$adj <- substitute(iKservS.L)
l$PT$adj <- substitute(ihLest)
e$PT$adj <- substitute(iUMP)
# UK unadjusted inputs
k$UK$unadj <- substitute(iKstkO.WwithRD)
l$UK$unadj <- substitute(iL)
e$UK$unadj <- substitute(iXp)
# UK quality-adjusted inputs
k$UK$adj <- substitute(iKservO.WwithRD)
l$UK$adj <- substitute(ihLest)
e$UK$adj <- substitute(iU)
# Time variables
t$PT <- substitute(iYear)
t$UK <- substitute(iYear)

countries <- c(substitute(PT), substitute(UK))
adjusteds <- c(substitute(unadj), substitute(adj))
energies <- c(substitute(noE), substitute(withE))
f <- list()
for (country in c(substitute(PT), substitute(UK))){
  for (adjusted in adjusteds){
    for (energy in energies){
      if (energy == substitute(noE)){
        eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + t$ctry, 
                        list(ctry=country, adjst=adjusted, ener=energy)))
      } else if (energy == substitute(withE)){
        eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + e$ctry$adjst + t$ctry, 
                        list(ctry=country, adjst=adjusted, ener=energy)))
      } else {
        stop(paste("Unknown energy", energy, "in loop for f"))
      }
    }
  }
}
